---
title: "Model creation and Evaluation"
author: "Nathan M"
date: "Sep 24, 2019"
output: ioslides_presentation
---


## Summary

The purpose of this application is for the user to easily select the variables to use in a linear model and then simply predict the mpg for a new car. While looking at a new car, we sometimes don't have all the information avaiable to make a perfect prediction of the mpg, so we'll use as many or as few variables that we have.

The linear model uses the selected variables to predict the mpg of a new car based on the inputs provided.

The regressions use the mtcars information provided in r


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Preliminary Look

An initial look at the data shows there are many variables that correlate with the mpg of a car

```{r cars, echo=FALSE}
  pairs(mtcars)
```


## Basic Summary

Using an ANOVA, we've down selected all of the variables in our linear model to only include the ones that correlate well with the final mpg (p<0.05)

These variables include:
1. Weight (wt)
2. Engine Displacement (disp)
3. Number of Cylinders (cyl)
4. Transmissions Type (am)

## The Final Model

The final Model:
```{r mod, eval=FALSE}
  lm(mpg~(wt+disp+cyl)*am, data=mtcars)
```

```{r modsum, echo=FALSE}
  summary(lm(mpg~(wt+disp+cyl)*am, data=mtcars))
```


